### 2016-12-16 paper/intro.tex
pass on intro

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both components can add up to the
aggregate cost of running a test suite, which can lead to late reports
of test failures.  Dealing with high testing costs is critical at
large IT organizations, with massive code and test bases.  The Google
TAP system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
system~\cite{prasad-shulte-ieee-microsoft-ci} provide evidence on the
criticality of the build and the testing processes at these
organizations.  Note, however, that the regression testing problem is
not specific to giants from the IT sector.  For example, a recent
paper from the automotive industry reported that test suites can take
days to run~\cite{artl-etal-icst2015}.

Several approaches have been proposed in the literature to address the
regression testing problem.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  It is important to note,
however, that balancing the test workload, either within or across
machines, is a popular, sound, and practical approach to address
testing cost and can't be neglected.  Furthermore, this approach is
complementary to those proposed in the literature. For example, as of
August 2013, the Groupon PWA system, which powers the
\url{groupon.com} website, included over 19K tests.  To run all those
tests under 10m, Groupon used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.  As additional examples, Google's TAP
and Microsoft's CloudBuild distribute task workloads in the cloud.
Note, that the alternative of renting a cloud
service\footnote{\url{https://clutch.co/cloud}} or even building a
server farm (for increased security) is a legitimate approach to
mitigate the regression testing problem at large organizations.
However, this solution may not be economically viable for smaller
projects with heavy testing loads.

@@

This paper focuses on optimizing regression testing of open-source
projects using commodity hardware.  This is an important problem
assuming that it is not rare for open-source projects to face high
testing costs.  \Fix{mention similar but different work} To the best
of our knowledge no prior work investigated this problem.

---- aqui

%% eventually move this to macros.tex
\newcommand{\numSubjs}{143}
\newcommand{\numLongRunning}{\Fix{17\%}}
\newcommand{\percentParallelForLongRunning}{\Fix{80\%}}

%Motivated by this potential gap in regression testing,

This paper focuses on the problem of understanding how critical the
regression testing problem is in open-source projects and what are the
potential benefits and shortcomings of using the parallelization
features of build systems and testing frameworks, which are very
popular today\Fix{cite cite cite}.  More precisely, we studied (1) how
prevalent long-running test suites are in open-source software
projects.  To conduct this experiment we selected \numSubjs{} Java
projects from github that are highly-popular and use the Maven build
system.  (Section~\ref{sec:eval} details our selection methodology.)
Our experimental results indicate that long-running test suites
(taking longer than 5m to complete\Fix{check if Ekstazi paper also
  used this value to indicate long runs and cite}) are not
rare~--~\numLongRunning{} of the projects we analyzed contain
long-running test suites.  \Mar{missing connection. why parallelism?}
From this result we investigated (2) how frequently the projects we
considered use parallelization to speedup test runs.  Our results
indicate that \percentParallelForLongRunning{} of long-running test
suites do use parallelism to speedup execution.  Given the popularity
of this solution, we further studied: (3) what are the causes of high
execution cost in individual tests (CPU vs. IO) and (4) how uniformly
cost is distributed across tests.  These questions help to assess the
impact of parallelization in test suite execution.  Intuitively,
IO-intensive test suites and test suites with uneven distribution of
cost per test are factors that limit the benefits of parallelization.
Results indicate that \Fix{...}  Finally, we investigated (5) what are
the limitations related to parallelization that could justify adoption
resistance.

>>>>

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both components can add up to the
aggregate cost of running a test suite, which can lead to late reports
of test failures.  Dealing with high testing costs is critical at
large IT organizations, with massive code and test bases.

Several approaches have been proposed in the literature to address the
regression testing problem.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  These approaches reduce testing
cost by reducing the amount of tests for execution.  It is important
to bring to light that the \emph{complementary alternative} of
balancing the test workload across work units is sound (\ie{}, it
cannot miss fault-revealing tests) and very popular in industry.
Evidence of this are the Google TAP system~\cite{google-tap,google-ci}
and Microsoft's CloudBuild
system~\cite{prasad-shulte-ieee-microsoft-ci}, which provide
distributed infrastructures to efficienctly build massive amounts of
code and run tests.  Note, however, that the regression testing
problem is not specific to giants from the IT sector.  For example, as
of August 2013, the Groupon PWA system, which powers the
\url{groupon.com} website, included over 19K tests.  To run all those
tests under 10m, Groupon used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.

%% As additional examples, Google's
%% TAP and Microsoft's CloudBuild distribute task workloads in the cloud.

At large organizations, the alternative of renting a cloud
service\footnote{\url{https://clutch.co/cloud}} or even building
proprietary infrastructures for running tests is a legitimate approach
to mitigate the regression testing problem.  However, for projects
with low budgets and yet moderate or heavy testing workloads, this
solution may not be economically viable.  The amount of serious
open-source project under development today is impressive.\Mar{give
  examples, provide stats.}  Optimizing existing computational
resources in this context saves money or time.  \Mar{what about free
  services (jenkins)?  how much can you scale execution and how
  expensive would that be?}

@@

\sloppy This paper focuses on the problem of understanding how
critical the regression testing problem is in open-source projects.
To the best of our knowledge no prior work investigated this problem,
which is important given the tremendous popularity of open-source
development and the wide impact of regression testing optimization
techniques in this setting.

%Motivated by this potential gap in regression testing,
%% More specifically, we studied how often long-running test suites occur
%% in this setting, how frequently parallelization features are used, if
%% not used why, and what are the associated drawbacks.

More precisely, we studied (1) how prevalent long-running test suites
are in open-source software projects.  To that end, we selected from
\github{} \numSubjs{} highly-popular Java projects containing Maven
build files.  (Section~\ref{sec:eval} details our selection
methodology.)  To run this experiment we used the default Maven
configuration to run a project's test suite and a 16GB memory i7-4790
Intel processor machine, which we carefully isolated.  Our results
indicate that the test suite of nearly one in every five projects from
our set (\percentMedLongRunning) takes at least 5m to run.  On
average, one of those test suites take \averageMedLongRunning{} to
run.  These results suggest that open-source projects often contain
long running test suites.

\Mar{missing connection. why
  parallelism?}  From this result we investigated (2) how frequently
the projects we considered use parallelization to speedup test runs.
Our results indicate that \percentParallelForLongRunning{} of
long-running test suites do use parallelism to speedup execution.
Given the popularity of this solution, we further studied: (3) what
are the causes of high execution cost in individual tests (CPU vs. IO)
and (4) how uniformly cost is distributed across tests.  These
questions help to assess the impact of parallelization in test suite
execution.  Intuitively, IO-intensive test suites and test suites with
uneven distribution of cost per test are factors that limit the
benefits of parallelization.  Results indicate that \Fix{...}
Finally, we investigated (5) what are the limitations related to
parallelization that could justify adoption resistance.
